Classification of Parkinson's disease patients using Bayesian deep learning based on fMRI data

### 2020-07-07 article.tex
Highlights added

%\begin{highlights}
%\item High accuracy with 
%\item Research highlights item 2
%\item Research highlights item 3
%\end{highlights}

>>>>

\begin{highlights}
\item We introduce a novel Bayesian Deep Convolutional Network for Parkinson's disease diagnosis.
\item The proposed method does not make assumptions about the disease or the dataset, making it a possible solution for other diseases.
\item Our model only relies on spatial information and ignores temporal information in the fMRI.
\item Computational costs of the proposed method is negligible compared to other existing methods. As a result, it is a widely applicable algorithm for low-end processors.
\item The experimental results confirm the high efficiency of the proposed method.
\end{highlights}
